Pteropod physiological analysis

### 2018-03-24 figures.Rmd
biomark table done

p4 <- ggplot() +
  geom_line(data = pl4[[1]], aes(x = pCO2, y = abu, group = O2, colour = O2), size = 1) + 
  geom_text(data = pl4[[2]], aes(x= x, y = y, label = lab), hjust = 0) +
  theme_bw() +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('Abundance') +
  ggtitle("(a) Positive additive effect of O2 on\npCO2 stress")

@@

>>>>

p4 <- ggplot() +
  geom_line(data = pl4[[1]], aes(x = pCO2, y = abu, group = O2, colour = O2), size = 1) + 
  geom_text(data = pl4[[2]], aes(x= x, y = y, label = lab), hjust = 0) +
  theme_bw() +
  scale_colour_gradientn(colours = cols) + 
  scale_y_continuous('Abundance') +
  ggtitle("(a) Synergistic effect of O2 on\npCO2 stress")

@@

```{r}
mods <- readxl::read_excel('raw/info for table.xlsx') %>% 
  .[-1, -1] %>% 
  gather('var', 'Model', everything()) %>% 
  mutate(
    org = ifelse(var %in% c('abundance', 'dissolution', 'length'), 'phy', 'bio'),
    Model = paste0('mod', Model)
    ) %>% 
  split(.$org)

biotab <- mods$bio %>% 
  left_join(biomod, by = 'Model') %>% 
  select(Model, data) %>%
  mutate(data = map(data, function(x){
    x %>% mutate(vr = seq(1:nrow(.)))
  })) %>% 
  unnest %>% 
  mutate(
    Model = gsub('mod', '', Model),
    Model = as.numeric(Model)
    ) %>% 
  group_by(Model) %>% 
  mutate(
    Pvl = gsub('ns', '', Pvl), 
    Rsq = ifelse(duplicated(Rsq), '', Rsq)
    ) %>% 
  ungroup %>% 
  unite('Est', Est, Pvl, sep = '') %>% 
  gather('estnm', 'estvl', Rsq, Est) %>% 
  unite('est', pte_lab, estnm, sep = ', ', remove = F) %>% 
  select(-estnm) %>% 
  split(.$pte_lab) %>%
  lapply(., function(x){

    out <- spread(x, est, estvl) %>% 
      select(-pte_lab) %>%
      arrange(Model, vr) %>% 
      select(-vr, -Model)

    if(!any(grepl('^LPX', names(out))))
      out <- out %>% 
        select(-env_lab)

    return(out)

  }) %>% 
  do.call('cbind', .) %>% 
  mutate(
    Model = rep(letters[1:(nrow(.)/3)], each = 3),
    Model = paste0('(', Model, ')'),
    Model = ifelse(duplicated(Model), '', Model)
  ) %>% 
  select(Model, everything())

names(biotab) <- gsub('^.*\\.', '', names(biotab))
vrs <- gsub('(^.*),\\s.*$', '\\1', names(biotab))
vrs[duplicated(vrs)] <- ''
vrs <- paste0(vrs, '<br>')
vrs[vrs %in% 'env_lab<br>'] <- 'Parameter<br>'
vrs2 <- gsub('^.*,\\s|Model|env_lab', '', names(biotab))
vrs <- paste(vrs, vrs2, sep = '')

names(biotab) <- vrs

knitr::kable(biotab)
```
